---
title: "Documentation"
author: "Jayshil"
date: "3 December 2019"
output: html_document
---
```{r}
print('Hello World!')
```

Alright, this was my first hands-on with R markdown. Hope it went well!!

***

# My R Documentation

'<-' is an assignment operator. For example,

```{r}
x <- 1
print(x)
x
msg <- 'Hello World'
print(msg)
# This is for comments
```

To create sequence use ':'. E.g.,

```{r}
x <- 1:20
x
```

Five objects of R:

* Character
* Numeric
* Integer
* Complex
* Boolean

A most basic object is a vector; contains objects of the same class

'List' can contain objects of different classes. This is an exception to the the vector class.

Empty vector can be created with the ```vector()``` function. It can have two arguments: First argument is the *class* of the object and the second would be the *length* of the object.

## Creating Vectors

The ```c()``` function can be used to create vectors of objects. 'c' stands for concatenate, because it can be used to concatenate things together.

```{r}
x <- c(0.5,0.6,0.7)   ## Numeric
y <- c("a", "b", "c") ## Character
z <- 1:7              ## Integer
w <- c(1+0i,2+3i)     ## Complex
xyzw = c(x,y,z,w)     ## Concatenate everything by making them string
vec = vector("numeric", length = 5)
x
y
z
w
xyzw
vec
```

To covert one class from another use ```as.***``` function. For example, let's convert numeric ```x``` from above example to character. However the insensical conversion don't work. That means the conversion of ```y``` from above example to numerica would results in ```NA``` to each components.

```{r}
x
yy = as.character(x)
zz = as.numeric(y)
yy
zz
```

To create a **list**, use a ```list()``` function as follows:

```{r}
ab = list(1, "ab", TRUE, 1+4i)
ab
```


